---
output: 
    md_document:
        variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Schemr

`schemr` is an R package for turning your photos into usable colour schemes for R visualisations.

The key driver is the `img_to_pallette` function, which:

- reads in images; 
- finds colour blobs within the image, representing the key highlighting colours; and
- uses affinity propagation clustering to condense the set of key colours.

### Example 1

First we have a look at a photo of me camping.
```{r }
library(OpenImageR)
library(magrittr)

# Read in the image
image <- readImage(path = "Images/camping.jpg")

# Shrink down the image
new_height <- dim(image)[1] * 0.4
new_width <- dim(image)[2] * 0.4
image %<>% resizeImage(image = ., width = new_width, height = new_height)

# Plot
plot(as.raster(image))

```

We see big blobs of blue and orange. Using schemr to extract these, we get:
```{r }
library(schemr)

# Extract key colours from image
schemr_image <- img_to_pallette(image_path = "Images/camping.jpg", resize_factor = 0.4,
                                verbose = FALSE)

# Plot the image
plot(schemr_image)

```

In addition, printing the class, shows the vector of hex RGB codes that make up the clustered data:

```{r }
schemr_image
```
